\section{Models and Preliminaries (Cont'd)}
\label{sec:model-preliminaries-contd}

\paragraph{Clock functionality.}
%
We adopt \funcClock (cf.~\cite{TCC:KMTZ13}) to model synchronous processors.
%
In a nutshell, \funcClock internally maintains a round variable $\tau$ which is only updatable when all parties send it the \textsc{clock-update} command.
%
Whenever a party \party is activated, \party sends a \textsc{clock-read} message to check the current round.
%
When round proceeds, \party executes the protocol and send \textsc{clock-update} after it completes all computations; if not, \party does nothing and wait for the next activation.
%
By interacting with \funcClock, parties are aware that they proceed in synchronized rounds.

\input{functionalities/global-clock}

\paragraph{Random oracle functionality.}
%
By convention, we model the hash function used to generate PoW as a random oracle; this is captured by the functionality \funcRO.

\input{functionalities/random-oracle}

Note that with regards to bounding access to real-world resources, functionality \funcRO as defined fails to limit the adversary on making a certain number of queries per round.
%
Hence, we adopt a functionality wrapper \cite{C:BMTZ17,EC:GKOPZ20} $\mathcal{W}(\funcRO)$ that wraps the corresponding resource to capture such restrictions.

\input{functionalities/wrapper-random-oracle}

\paragraph{Diffusion functionality.}
%
We model the synchronous communication by \funcDiffuse \cite{C:BMTZ17}.
%
Note that we present $\funcDiffuse^\delay$ which is parameterized by the network delay \delay, and the synchronous variant can be easily derived by setting $\delay = 1$.

\input{functionalities/diffuse}

\paragraph{Common reference string functionality.}
%
We model a public setup by the CRS functionality \funcCRS.

\input{functionalities/crs}
