\section{Application: Fast State Machine Replication}
\label{sec:fast-state-machine-replication}

We now show how to adapt the sequential composition approach in~\cref{subsec:fast-sequential-composition} to implement a state machine replication (SMR) protocol.
%
Our resulting protocol achieves both Consistency and expected-constant-time Liveness for all types of transactions (including conflicting ones).
%
Namely, for any transaction \tx, when \tx is diffused to all honest participants (miners), it takes in expectation a constant number of rounds to get settled into the immutable final ledger.

We first give our definition of SMR, and elaborate on why fast SMR protocol cannot be directly derived from the sequential composition of multi-valued Chain-King Consensus.
%
Then, in~\cref{subsec:fast-state-machine-replication} we propose a new method that introduces randomness to the output of the king chain and helps circumvent the above problem while preserving expected-constant settlement time for all types of transactions.
%
Finally, in~\cref{subsec:bootstrapping-from-genesis} we show how a third party observer, joining in the middle of the protocol, can catch up with honest parties and learn the state of the ledger.

\paragraph{SMR background.}
%
State machine replication (SMR) is the problem of distributing the operation of a state machine across a set of replicas so that the operation of the machine is resilient to failure of a subset of the replicas.
%
This concept was originally described in~\cite{CACM:Lamport78},
%
and later further elaborated on by Schneider \cite{CSUR:Schneider90} where a high-level description of SMR was provided.
%
Blockchain protocols, and in particular Bitcoin's~\cite{Nak08} have renewed interest in SMR definitions and constructions, as they can be seen as a way to realize SMR in a setting where there is no predetermined set of replicas.
%
This has been studied and formalized in a series of works (e.g., \cite{EPRINT:GarKiaLeo14,EC:PasSeeash17,RSA:GarKia20}).

We now give a concise definition of SMR.
%
A number of $n$ servers, a subset \honestPartySet of which is assumed to be non-faulty, maintain a log of transactions, denoted $\mathsf{Log}$.
%
The log of each server also timestamps each transaction.
%
The notation $\mathsf{Log}_i[t]$  denotes the log of the server $\party_i$ up to time $t$.
%
Furthermore, it is assumed that each server has a buffer for incoming transactions, denoted by $I_i[t]$, that are valid with respect to its view (invalid transactions are dropped).
%
Finally, and for simplicity, assume that all well-formed transactions are admissible in the log. In SMR, the following two conditions must be satisfied:

\begin{cccItemize}[noitemsep]
      \item \textbf{Consistency:} $\forall \party_i, \party_j \in \honestPartySet$ (where not necessarily $i \neq j$) and $t, t'$ it holds that $ \mathsf{Log}_i[t]  \preceq \mathsf{Log}_j [t']$ or $\mathsf{Log}_j [t'] \preceq  \mathsf{Log}_i[t]$.
      
      \item \textbf{Liveness:} There is a parameter $u\in\mathbb{N}$ for which the following holds: $(\forall \party_i \in \honestPartySet : \tx \in I_i[t] ) \implies \tx \in \mathsf{Log}_i[t + u]$.
\end{cccItemize}

Typically, the Liveness parameter $u$ is a pre-defined value according to the protocol parameterization.
%
It is natural to extend the notion and allow $u$ to be a random variable with a distribution that depends on the specific parameterization.
%
I.e., given a transaction \tx appearing in all honest buffers at time $t$, the probability that it is included in all honest logs at time $t + u$ shares the same distribution with $u$.
%
In our protocol, we achieve $u$ with a geometric distribution, hence the time for \tx to get installed in the immutable ledger is expected-constant.

Note that there are more properties of interest for SMR, such as \emph{observability}, which is the requirement that a third party observer be capable of interpreting correctly the current state of the ledger by inspecting the logs of the servers.

\input{content/applications/fast-state-machine-replication}
\input{content/applications/bootstrap-from-genesis}